The future age structure of scientific disciplines

### 2025-04-14 age_structure_forecasts.qmd
Working on converting quarto doc figures

```{r setup, include=FALSE}
#| eval: true
library(ggplot2)
library(patchwork)
library(knitr)
library(kableExtra)

@@

```{r}
#| label: fig-labour-force
#| fig-cap: Labour force participation rates by one-year age groups for 2016 and 2021, along with the average of these two years, which is used as a proxy for 2006 and 2011.
tar_read(fig1)
```

@@

```{r}
#| label: fig-census
#| fig-cap: Distribution of scientists active in the labour market by age across  Census years (2006, 2011, 2016, 2021).
tar_read(fig2)
```

```{r}
#| label: fig-cohort-interpolation
#| fig-cap: Interpolated number of scientists in Australia, 2006–2021, using linear cohort interpolation.
tar_read(fig3)
```

@@

```{r}
#| label: fig-beforedisaggregation
#| fig-cap: Retirement intentions for key industries before smoothed disaggregation.
tar_read(fig4)
```

```{r}
#| label: fig-afterdisaggregation
#| fig-cap: Retirement intentions across key industries after smoothed disaggregation.
tar_read(fig5)
```

@@

The data show that a significant portion of workers plan to retire between the ages of 60 and 70. This distribution of retirement ages exhibits positive kurtosis, with the highest peak at age 67, where 13.16% of workers indicate their intention to retire, as shown in @fig-retirements and summarised in @tbl-retirements.

```{r}
#| label: fig-retirements
#| fig-cap: Age distribution of retirement intentions for the 2022--2023 Australian financial year.
ggplot(retirement_science) +
  aes(x = Age, y = pc) +
  geom_line() +
  labs(y = "Percentage of retirement intentions",
       title = "Retirement Intentions",
       subtitle = "Natural and Physical Sciences\n2022–23 Financial Year") +
  scale_x_continuous(breaks = seq(40, 100, by = 10)) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5)
  )
```

```{r}
#| label: tbl-retirements
#| tbl-cap: Percentage distribution of retirement intentions for ages 64-69 for the Australian financial year 2022--2023.

retirement_science |>
  filter(Age >= 64 & Age <= 69) |>
  mutate(pc = paste0(round(pc, 2), "%")) |>
  select(Age, pc) |>
  kable(col.names = c("Age", "Percentage of Retirement Intentions"), align = "c") |>
  add_header_above(c("Percentage of Retirement Intentions Ages 64–69" = 2), bold = TRUE) |>
  kable_styling(latex_options = c("striped"))
```

@@

```{r}
#| label: fig-retirements2
#| fig-cap: Age-specific probability of retirement based on the 2022--2023 Australian financial year.
retirement_science |>
  filter(Age < 100) |>
  ggplot() +
  aes(x = Age, y = retire_prob) +
  geom_line() +
  labs(y = "Probability of retirement",
    title = "Probability of Retirement",
    subtitle = "Natural and Physical Sciences\n2022–23 Financial Year"
  ) +
  scale_x_continuous(breaks = seq(40, 100, by = 10)) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5)
  )
```

@@

```{r}
#| label: fig-death-probs
#| fig-cap: Age-specific probabilities of death (on a logarithmic scale) for each year from 1971 to 2021.
aus_death_prob |>
  autoplot(death_prob) +
  scale_y_log10(labels = scales::label_number()) +
  labs(y = "Log-scaled probability of death") +
  labs(
    title = "Australian Mortality-Based Death Probabilities",
    subtitle = "1971 - 2021"
  ) +
  scale_x_continuous(breaks = seq(0, 100, by = 10)) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5)
  )
```

@@

```{r}
#| label: fig-completions1
#| fig-cap: Percentage distribution of graduate completions by age for each year from 2006 to 2023.

completions_step |>
  ggplot() +
  aes(x = Age, y = pc, colour = Year, group = Year) +
  geom_line() +
  scale_color_gradientn(colours = rainbow(10)[1:8]) +
  labs(
    y = "Percentage of graduates",
    title = "Graduate Completions by Year and Age",
    subtitle = "2006 - 2023"
  ) +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  scale_y_continuous(
    labels = scales::percent_format(scale = 1)
  ) +
  theme_classic()  +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5)
  )
```

@@

```{r}
#| label: fig-completions2
#| fig-cap: Percentage distribution of graduate completions by age, aggregated over the years 2006 to 2023.
ave_completions |>
  ggplot() +
  aes(x = Age, pc) +
  geom_line() +
  labs(y = "Percentage of graduates") +
  labs(
    title = "Graduate Completions by Age",
    subtitle = "2006 - 2023"
  ) +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5)
  )
```

@@

```{r}
#| label: tbl-completions
#| tbl-cap: Percentage distribution of graduate completions for ages 20-25 for the years 2006 to 2023.

ave_completions |>
  filter(Age >= 20 & Age <= 25) |>
  mutate(pc = paste0(round(pc, 2), "%")) |>
  select(Age, pc) |>
  kable(col.names = c("Age", "Percentage of Graduates"), align = "c") |>
  add_header_above(c("Percentage of Graduates Ages 20-25" = 2), bold = TRUE) |>
  kable_styling(latex_options = c("striped"))
```

@@

```{r}
#| label: fig-physicists
#| fig-cap: The number of scientists in Physics and Astronomy active in the Australian labour market, shown by age, as recorded in the Australian Census for the years 2006, 2011, 2016, and 2021.
years <- seq(2006, 2021, by = 5)
cols <- c("#FF6F00", "#009E73", "#009DFF", "#FF00BF")
names(cols) <- years
physics_and_astronomy |>
  as_tibble() |>
  filter(Year %in% years) |>
  mutate(Year = factor(Year, levels = rev(years))) |>
  ggplot() +
  aes(x = Age, y = Working, color = Year, group = Year) +
  geom_line() +
  labs(y = "Number of active scientists") +
  scale_color_manual(values = cols, name = "Census Year") +
  labs(
    title = "Working Population",
    subtitle = "Physics and Astronomy"
  ) +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  theme_classic()  +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5)
  )
```

```{r}
#| label: fig-physicists2
#| fig-cap: Interpolated number of scientists in Physics and Astronomy active in the Australian labour market, 2006–2021, using linear cohort interpolation.
physics_and_astronomy |>
  autoplot(Working) +
  labs(y = "Number of active scientists") +
  labs(
    title = "Interpolated Working Population",
    subtitle = "Physics and Astronomy\n2006 - 2021"
  ) +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  theme_classic()  +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5)
  )
```

```{r}
#| label: tbl-stats-physics
#| tbl-cap: Summary statistics of physicists and astronomers active in the Australian labour market as recorded in the Australian Census for the years 2006, 2011, 2016, and 2021.

weighted_percentile <- function(x, w, prob) {
  o <- order(x)
  x <- x[o]
  w <- w[o]
  cumsum_w <- cumsum(w) / sum(w)
  x[min(which(cumsum_w >= prob))]
}

statistics <- physics_and_astronomy |>
  as_tibble() |>
  filter(Year %in% years) |>
  mutate(Age = as.numeric(as.character(Age))) |>
  group_by(Year) |>
  summarise(
    `10th Percentile Age` = weighted_percentile(Age, Working, prob = 0.1),
    `90th Percentile Age` = weighted_percentile(Age, Working, prob = 0.9),
    `Weighted Average Age` = round(sum(Age * Working, na.rm = TRUE) / sum(Working, na.rm = TRUE), 1),
    `Weighted Median Age` = weighted_percentile(Age, Working, prob = 0.5)
  )

kable(statistics, align = "c") |>
  add_header_above(c("Summary Statistics of Physics and Astronomy" = ncol(statistics)), bold = TRUE) |>
  kable_styling(latex_options = c("striped"))
```

@@

```{r}
#| label: fig-physics-leavers
#| fig-cap: Annual number of graduates in Physics and Astronomy, 2006–2023.
ggplot(course_leavers_lvl4 |> filter(discipline == "Physics and Astronomy"), aes(x = Year, y = Graduates)) +
  geom_line() +
  scale_x_continuous(breaks = seq(2006, 2023, by = 2)) +
  labs(
    title = "Graduates",
    subtitle = "Physics and Astronomy\n2006–2023",
    y = "Number of graduates"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5)
  )
```

```{r}
#| label: fig-future-grads-physics
#| fig-cap: Projected number of Physics and Astronomy graduates, 2024–2041, with 90% prediction intervals, based on historical data from 2006–2023.
physics_grads <- future_course_leavers_science |>
  filter(discipline == "Physics and Astronomy") |>
  summarise(
    mean = mean(Graduates),
    lo = quantile(Graduates, prob = 0.05),
    hi = quantile(Graduates, prob = 0.95)
  )
ggplot(physics_grads) +
    aes(x = Year) +
    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
    geom_line(aes(y = mean), color = "#c14b14") +
    geom_line(data = course_leavers_lvl4 |> filter(discipline == "Physics and Astronomy"), aes(y = Graduates)) +
  labs(y = "Number of graduates",
       title = "Forecast of Graduates",
    subtitle = "Physics and Astronomy\nForecasted Years: 2024–2041"
  ) +
 scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
  theme_classic()  +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5)
  )
```

@@

```{r}
#| label: fig-net-migrants
#| fig-cap: Net migration of scientists in Physics and Astronomy by age, 2006–2020.
physics_and_astronomy |>
  autoplot(Migrants) +
  scale_x_continuous(breaks = seq(10,100,by=10)) +
  labs(
    y = "Number of net migrants",
    title = "Estimated Net Migration",
    subtitle = "Physics and Astronomy\n2006 - 2020"
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha=0.5) +
  theme_classic()  +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5)
  )
```

@@

```{r}
#| label: fig-future-physics
#| fig-height: 3
#| fig-cap: Two example simulations from a set of 500, using historical data from 2006-2021 to forecast age-specific population distributions for 2022-2041.
p <- physics_and_astronomy |>
  ggplot() +
  aes(x = Age, y = Working, group = Year) +
  geom_line(colour = "gray")
p1 <- p +
  geom_line(data = future_physics_and_astronomy |> filter(.rep == "1"), aes(colour = Year)) +
  labs(y = "Number of working scientists") +
  scale_color_gradientn(colors = rainbow(10)[1:8]) +
  labs(
    title = "Simulation 1",
    subtitle = "Forecasted Years: 2022 - 2041"
  ) +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  theme_classic()  +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5),
    legend.position = "none"  # Remove legend
  )

@@

```{r}
#| label: fig-future-physics-2035
#| fig-cap: Forecasted age distribution of the working population for Physics and Astronomy in 2025 and 2035, comparing changes over 10 years. Shaded areas represent 90% prediction intervals.

@@

```{r}
#| label: fig-total-future-physics
#| fig-cap: Forecasted total number of working scientists for Physics and Astronomy (2022–2041), indicating the rate of change. Shaded areas represent 90% prediction intervals.

@@

```{r}
#| label: fig-working-population
#| fig-cap: "Age distribution of the working population across scientific disciplines based on Census data from 2006, 2011, 2016, and 2021. Each panel represents a different discipline, with lines indicating the number of active scientists in the Australian labour market by age for each Census year."
#| fig-height: 5.5
disciplines_combined <- bind_rows(
  as_tibble(physics_and_astronomy) |> mutate(Discipline = "Physics and Astronomy"),
  as_tibble(mathematical_sciences) |> mutate(Discipline = "Mathematical Sciences"),
  as_tibble(chemical_sciences) |> mutate(Discipline = "Chemical Sciences"),
  as_tibble(earth_sciences) |> mutate(Discipline = "Earth Sciences"),
  as_tibble(biological_sciences) |> mutate(Discipline = "Biological Sciences"),
  as_tibble(other_natural_and_physical_sciences) |> mutate(Discipline = "Other Natural and Physical Sciences"),
  as_tibble(natural_and_physical_sciences__nfd) |> mutate(Discipline = "Natural and Physical Sciences (n.f.d.)")
)

@@

```{r}
#| label: fig-interpolated-working-population
#| fig-cap: "Age distribution of the working population across scientific disciplines, interpolated from Census data between 2006 and 2021. Each panel represents a different discipline, with lines indicating the number of active scientists in the Australian labour market by age and year."
#| fig-height: 6
ggplot(disciplines_combined) +
  aes(x = Age, y = Working, group = Year, color = Year) +
  geom_line() +
  facet_wrap(~Discipline, scales = "free_y") +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  scale_color_gradientn(
    colours = rainbow(10)
  ) +
  labs(
    y = "Number of active scientists",
    title = "Interpolated Working Population by Discipline",
    subtitle = "Natural and Physical Sciences\n2006 - 2021"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5),
    legend.position = "top"
  )
```

@@

```{r}
#| label: fig-graduates-disciplines
#| fig-cap: "Number of graduates across scientific disciplines from 2006 to 2023. Each panel represents a different discipline, showing the trend in graduate numbers over time."

@@

```{r}
#| label: fig-net-migration-disciplines
#| fig-cap: Estimated net migration by age across scientific disciplines (2006–2020). Each panel represents a different discipline, showing net migration trends across age groups.
#| fig-height: 6
ggplot(disciplines_combined) +
  aes(x = Age, y = Migrants, group = Year, color = Year) +
  geom_line() +
  facet_wrap(~Discipline, scales = "free_y") +
  scale_x_continuous(breaks = seq(10, 100, by = 10)) +
  scale_color_gradientn(
    colours = rainbow(10)
  ) +
  labs(
    y = "Number of net migrants",
    title = "Estimated Net Migration by Discipline",
    subtitle = "Natural and Physical Sciences\n2006 - 2020"
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5),
    legend.position = "top"
  )
```

@@

```{r}
#| label: fig-forecast-working-population
#| fig-cap: "Projected age distribution of the working population in 2025 and 2035 across scientific disciplines. The shaded regions represent the 90% prediction intervals, and the solid lines indicate the mean estimates for each year."
#| fig-height: 5.5
future_disciplines_combined <- bind_rows(
  as_tibble(future_physics_and_astronomy) |> mutate(Discipline = "Physics and Astronomy"),
  as_tibble(future_mathematical_sciences) |> mutate(Discipline = "Mathematical Sciences"),
  as_tibble(future_chemical_sciences) |> mutate(Discipline = "Chemical Sciences"),
  as_tibble(future_earth_sciences) |> mutate(Discipline = "Earth Sciences"),
  as_tibble(future_biological_sciences) |> mutate(Discipline = "Biological Sciences"),
  as_tibble(future_other_natural_and_physical_sciences) |> mutate(Discipline = "Other Natural and Physical Sciences"),
  as_tibble(future_natural_and_physical_sciences__nfd) |> mutate(Discipline = "Natural and Physical Sciences (n.f.d.)")
)

@@

```{r}
#| label: fig-forecast-total-working-scientists
#| fig-cap: "Projected total number of working scientists across scientific disciplines from 2022 to 2041. The shaded region represents the 90% prediction interval, the coloured line indicates the mean estimate, and the black line represents historical data."

@@

# Broader Applications: Beyond Natural and Physical Sciences {#broader-applications}

The forecasting process can be applied to any ASCED educational field. This section demonstrates its broader applicability by extending the analysis to three additional Broad Fields: Information Technology, Engineering and Related Technologies, and Agriculture, Environmental, and Related Studies. As each field presents different industry characteristics, the retirement intentions data is adjusted accordingly. Forecasts for all disciplines within each Broad Field offer a comprehensive view of workforce trends across these areas.

## Information Technology

```{r eval=FALSE }
#| label: fig-working-population-infotech
#| fig-cap: "Age distribution of the working population across Information Technology disciplines based on Census data from 2006, 2011, 2016, and 2021. Each panel represents a different discipline, with lines indicating the number of active IT professionals in the Australian labour market by age for each Census year."

disciplines_combined <- bind_rows(
  as_tibble(computer_science) |> mutate(Discipline = "Computer Science"),
  as_tibble(information_systems) |> mutate(Discipline = "Information Systems"),
  as_tibble(other_information_technology) |> mutate(Discipline = "Other"),
  as_tibble(information_technology__nfd) |> mutate(Discipline = "Not Further Defined")
)

disciplines_combined$Discipline <- factor(
  disciplines_combined$Discipline,
  levels = c("Computer Science", "Information Systems", "Other", "Not Further Defined")
)

disciplines_combined |>
  filter(Year %in% years) |>
  mutate(Year = factor(Year, levels = rev(years))) |>
  ggplot() +
  aes(x = Age, y = Working, color = Year, group = Year) +
  geom_line() +
  scale_color_manual(values = cols) +
  labs(
    y = "Number of active IT professionals",
    title = "Working Population by Discipline",
    subtitle = "Census Years: 2006, 2011, 2016, 2021"
  ) +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  facet_wrap(~Discipline, scales = "free_y") +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5),
    legend.position = "top"
  )
```

```{r eval=FALSE  }
#| label: fig-graduates-disciplines-infotech
#| fig-cap: "Number of graduates across information technology disciplines from 2006 to 2023. Each panel represents a different discipline, showing the trend in graduate numbers over time."

course_leavers_arranged <- course_leavers_lvl4_infotech

ggplot(course_leavers_arranged) +
  aes(x = Year, y = Graduates) +
  geom_line() +
  facet_wrap(~discipline, scales = "free_y") +
  labs(
    y = "Number of graduates",
    title = "Graduates Across Disciplines",
    subtitle = "Years: 2006 - 2023"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5),
    legend.position = "none"
  )
```

In the 2022-2023 financial year, the majority of Information Technology workers were employed in the Professional, Scientific, and Technical Services industry, accounting for 28.89% of the workforce. For forecasting retirement trends, the retirement intentions data from this industry serves as the basis.

In @fig-forecast-working-population-infotech, the forecasts for the Information Technology disciplines show the following workforce trends from 2025 to 2035:

-   **Computer Science** *(Expansive Workforce):* Workforce growth is observed, particularly in the 30–40 age range and significantly in the 50–70 range. The higher average forecast reflects both expansion and delayed retirements.
-   **Information Systems** *(Uncertain Workforce):* Extremely large prediction intervals are present at workforce entry due to low current workforce numbers but high graduate inflows. The projected workforce remains relatively small on average, with estimates indicating fewer individuals aged 45 in the workforce by 2035.
-   **Other Information Technology** *(Uncertain Workforce):* Workforce projections show extreme uncertainty. Despite large graduate inflows, the projected workforce remains small, and the absence of prediction intervals indicates a lack of certainty in future participation.
-   **Information Technology (n.f.d.)** *(Expansive Workforce):* Workforce growth is expected in the 35–45 age range, with a significant increase in the 50–70 age group, reflecting sustained participation among older workers.

```{r}
#| label: fig-forecast-working-population-infotech
#| fig-cap: "Projected age distribution of the working population in 2025 and 2035 across IT disciplines. The shaded regions represent the 90% prediction intervals, and the solid lines indicate the mean estimates for each year."
#| fig-height: 4.5

future_disciplines_combined <- bind_rows(
  as_tibble(future_computer_science) |> mutate(Discipline = "Computer Science"),
  as_tibble(future_information_systems) |> mutate(Discipline = "Information Systems"),
  as_tibble(future_other_information_technology) |> mutate(Discipline = "Other"),
  as_tibble(future_information_technology__nfd) |> mutate(Discipline = "Not Further Defined")
)

future_disciplines_combined$Discipline <- factor(
  future_disciplines_combined$Discipline,
  levels = c("Computer Science", "Information Systems", "Other", "Not Further Defined"
))

# 2025 and 2035
eg_forecast <- future_disciplines_combined |>
  filter(Year %in% c(2025, 2035), Working >= 0) |>
  group_by(Discipline, Age, Year) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )

# Overlay
ggplot(eg_forecast) +
    aes(x = Age, color = factor(Year)) +
    geom_ribbon(aes(ymin = lo, ymax = hi, fill = factor(Year)), alpha = 0.1) +
    geom_line(aes(y = mean), size = 0.75) +
    labs(
      y = "Number of working IT professionals",
      title = "Forecast of Working Population by Discipline",
      subtitle = "Information Technology",
      color = "Forecast Year",
      fill = "Forecast Year"
    ) +
    scale_color_manual(values = c("2025" = "#66666644", "2035" = "#c14b14")) +
    scale_fill_manual(values = c("2025" = "#66666644", "2035" = "#c14b1444")) +
    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
    theme_classic() +
    theme(
      plot.title = element_text(hjust = 0.5, face = "bold"),
      plot.subtitle = element_text(hjust = 0.5),
      legend.position = "top"
    ) +
    facet_wrap(~Discipline, scales = "free_y", ncol = 3)
```

The Information Technology workforce consists of both expansive and uncertain disciplines. Computer Science and Information Technology (n.f.d.) exhibit workforce growth across multiple age groups, including delayed retirements beyond 60. In contrast, Information Systems and Other Information Technology show significant uncertainty, where high graduate inflows contrast with low workforce numbers, leading to substantial forecast variability.

Unlike other Information Technology disciplines that cover multiple fields, Other Information Technology consists solely of Security Science, a single, specialised field. Historically, its workforce was minimal in 2006 and 2011, with some growth in 2016 and 2021. Despite thousands of graduates, the projected workforce remains relatively small. This mismatch between graduate numbers and workforce participation introduces substantial uncertainty. Since the model relies on graduate inflows, this occurs when historical workforce participation is low, and graduates do not transition into the workforce as expected. This reflects the characteristics of the available data rather than a limitation of the model.

The absence of a prediction interval despite the presence of an average further highlights this uncertainty. The data range is so large that both the lower and upper bounds collapse to zero, even though the true range is much wider. While this may make the forecast appear incomplete, it actually reflects extreme variability in workforce participation. Understanding the underlying cause would require external data, such as why Security Science sees consistently high graduate numbers despite low workforce participation, how ASCED classifies this discipline, or whether industry demand, employment pathways, or policy incentives influence trends.

In @fig-forecast-total-working-it, Computer Science and Information Technology (n.f.d.) are experiencing workforce growth. Information Systems indicates a potential decline on average, though the large prediction intervals in later years suggest possible expansion. Other Information Technology remains highly unpredictable, with no clear alignment between the average and the prediction interval.

```{r}
#| label: fig-forecast-total-working-it
#| fig-cap: "Projected total number of working IT professionals across IT disciplines from 2022 to 2041. The shaded region represents the 90% prediction interval, the coloured line indicates the mean estimate, and the black line represents historical data."
#| fig-height: 4

disciplines_combined <- bind_rows(
  as_tibble(computer_science) |> mutate(Discipline = "Computer Science"),
  as_tibble(information_systems) |> mutate(Discipline = "Information Systems"),
  as_tibble(other_information_technology) |> mutate(Discipline = "Other"),
  as_tibble(information_technology__nfd) |> mutate(Discipline = "Not Further Defined")
)

disciplines_combined$Discipline <- factor(
  disciplines_combined$Discipline,
  levels = c("Computer Science", "Information Systems", "Other", "Not Further Defined")
)

>>>>

```{r setup, include=FALSE}
#| eval: true
library(targets)

@@

```{r}
#| label: fig-labour-force
#| eval: true
#| fig-cap: Labour force participation rates by one-year age groups for 2016 and 2021, along with the average of these two years, which is used as a proxy for 2006 and 2011.
tar_read(fig1)
```

@@

```{r}
#| label: fig-census
#| eval: true
#| fig-cap: Distribution of scientists active in the labour market by age across  Census years (2006, 2011, 2016, 2021).
tar_read(fig2)
```

```{r}
#| label: fig-cohort-interpolation
#| eval: true
#| fig-cap: Interpolated number of scientists in Australia, 2006–2021, using linear cohort interpolation.
tar_read(fig3)
```

@@

```{r}
#| label: fig-beforedisaggregation
#| eval: true
#| fig-cap: Retirement intentions for key industries before smoothed disaggregation.
tar_read(fig4)
```

```{r}
#| label: fig-afterdisaggregation
#| eval: true
#| fig-cap: Retirement intentions across key industries after smoothed disaggregation.
tar_read(fig5)
```

@@

The data show that a significant portion of workers plan to retire between the ages of 60 and 70. This distribution of retirement ages exhibits positive kurtosis, with the highest peak at age 67, where 13.16% of workers indicate their intention to retire, as shown in @fig-retirements.

```{r}
#| label: fig-retirements
#| eval: true
#| fig-cap: Age distribution of retirement intentions for the 2022--2023 Australian financial year.
tar_read(fig6)
```

@@

```{r}
#| label: fig-retirements2
#| eval: true
#| fig-cap: Age-specific probability of retirement based on the 2022--2023 Australian financial year.
tar_read(fig7)
```

@@

```{r}
#| label: fig-death-probs
#| eval: true
#| fig-cap: Age-specific probabilities of death (on a logarithmic scale) for each year from 1971 to 2021.
tar_read(fig8)
```

@@

```{r}
#| label: fig-completions1
#| eval: true
#| fig-cap: Percentage distribution of graduate completions by age for each year from 2006 to 2023.
tar_read(fig9)
```

@@

```{r}
#| label: fig-completions2
#| eval: true
#| fig-cap: Percentage distribution of graduate completions by age, aggregated over the years 2006 to 2023.
tar_read(fig10)
```

@@

```{r}
#| label: tbl-completions
#| eval: true
#| tbl-cap: Percentage distribution of graduate completions for ages 20-25 for the years 2006 to 2023.
tar_read(tab2)
```

@@

```{r}
#| label: fig-physicists
#| fig-cap: The number of scientists in Physics and Astronomy active in the Australian labour market, shown by age, as recorded in the Australian Census for the years 2006, 2011, 2016, and 2021.
#| eval: true
tar_read(fig11)
```

```{r}
#| label: fig-physicists2
#| eval: true
#| fig-cap: Interpolated number of scientists in Physics and Astronomy active in the Australian labour market, 2006–2021, using linear cohort interpolation.
tar_read(fig12)
```

@@

```{r}
#| label: fig-physics-leavers
#| eval: true
#| fig-cap: Annual number of graduates in Physics and Astronomy, 2006–2023.
tar_read(fig13)
```

```{r}
#| label: fig-future-grads-physics
#| fig-cap: Projected number of Physics and Astronomy graduates, 2024–2041, with 90% prediction intervals, based on historical data from 2006–2023.
#| eval: true
tar_read(fig14)
```

@@

```{r}
#| label: fig-net-migrants
#| eval: true
#| fig-cap: Net migration of scientists in Physics and Astronomy by age, 2006–2020.
tar_read(fig15)
```

@@

```{r}
#| label: fig-future-physics
#| eval: false
#| fig-height: 3
#| fig-cap: Two example simulations from a set of 500, using historical data from 2006-2021 to forecast age-specific population distributions for 2022-2041.
p <- physics_and_astronomy |>
  ggplot() +
  aes(x = Age, y = Working, group = Year) +
  geom_line(colour = "gray")
p1 <- p +
  geom_line(data = future_physics_and_astronomy |> filter(.rep == "1"), aes(colour = Year)) +
  labs(y = "Number of working scientists") +
  scale_color_gradientn(colors = rainbow(10)[1:8]) +
  labs(
    title = "Simulation 1",
    subtitle = "Forecasted Years: 2022 - 2041"
  ) +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  theme_classic()  +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5),
    legend.position = "none"  # Remove legend
  )

@@

```{r}
#| label: fig-future-physics-2035
#| eval: false
#| fig-cap: Forecasted age distribution of the working population for Physics and Astronomy in 2025 and 2035, comparing changes over 10 years. Shaded areas represent 90% prediction intervals.

@@

```{r}
#| label: fig-total-future-physics
#| eval: false
#| fig-cap: Forecasted total number of working scientists for Physics and Astronomy (2022–2041), indicating the rate of change. Shaded areas represent 90% prediction intervals.

@@

```{r}
#| label: fig-working-population
#| eval: false
#| fig-cap: "Age distribution of the working population across scientific disciplines based on Census data from 2006, 2011, 2016, and 2021. Each panel represents a different discipline, with lines indicating the number of active scientists in the Australian labour market by age for each Census year."
#| fig-height: 5.5
disciplines_combined <- bind_rows(
  as_tibble(physics_and_astronomy) |> mutate(Discipline = "Physics and Astronomy"),
  as_tibble(mathematical_sciences) |> mutate(Discipline = "Mathematical Sciences"),
  as_tibble(chemical_sciences) |> mutate(Discipline = "Chemical Sciences"),
  as_tibble(earth_sciences) |> mutate(Discipline = "Earth Sciences"),
  as_tibble(biological_sciences) |> mutate(Discipline = "Biological Sciences"),
  as_tibble(other_natural_and_physical_sciences) |> mutate(Discipline = "Other Natural and Physical Sciences"),
  as_tibble(natural_and_physical_sciences__nfd) |> mutate(Discipline = "Natural and Physical Sciences (n.f.d.)")
)

@@

```{r}
#| label: fig-interpolated-working-population
#| fig-cap: "Age distribution of the working population across scientific disciplines, interpolated from Census data between 2006 and 2021. Each panel represents a different discipline, with lines indicating the number of active scientists in the Australian labour market by age and year."
#| fig-height: 6
#| eval: false
ggplot(disciplines_combined) +
  aes(x = Age, y = Working, group = Year, color = Year) +
  geom_line() +
  facet_wrap(~Discipline, scales = "free_y") +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  scale_color_gradientn(
    colours = rainbow(10)
  ) +
  labs(
    y = "Number of active scientists",
    title = "Interpolated Working Population by Discipline",
    subtitle = "Natural and Physical Sciences\n2006 - 2021"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5),
    legend.position = "top"
  )
```

@@

```{r}
#| label: fig-graduates-disciplines
#| eval: false
#| fig-cap: "Number of graduates across scientific disciplines from 2006 to 2023. Each panel represents a different discipline, showing the trend in graduate numbers over time."

@@

```{r}
#| label: fig-net-migration-disciplines
#| eval: false
#| fig-cap: Estimated net migration by age across scientific disciplines (2006–2020). Each panel represents a different discipline, showing net migration trends across age groups.
#| fig-height: 6
ggplot(disciplines_combined) +
  aes(x = Age, y = Migrants, group = Year, color = Year) +
  geom_line() +
  facet_wrap(~Discipline, scales = "free_y") +
  scale_x_continuous(breaks = seq(10, 100, by = 10)) +
  scale_color_gradientn(
    colours = rainbow(10)
  ) +
  labs(
    y = "Number of net migrants",
    title = "Estimated Net Migration by Discipline",
    subtitle = "Natural and Physical Sciences\n2006 - 2020"
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5),
    legend.position = "top"
  )
```

@@

```{r}
#| label: fig-forecast-working-population
#| eval: false
#| fig-cap: "Projected age distribution of the working population in 2025 and 2035 across scientific disciplines. The shaded regions represent the 90% prediction intervals, and the solid lines indicate the mean estimates for each year."
#| fig-height: 5.5
future_disciplines_combined <- bind_rows(
  as_tibble(future_physics_and_astronomy) |> mutate(Discipline = "Physics and Astronomy"),
  as_tibble(future_mathematical_sciences) |> mutate(Discipline = "Mathematical Sciences"),
  as_tibble(future_chemical_sciences) |> mutate(Discipline = "Chemical Sciences"),
  as_tibble(future_earth_sciences) |> mutate(Discipline = "Earth Sciences"),
  as_tibble(future_biological_sciences) |> mutate(Discipline = "Biological Sciences"),
  as_tibble(future_other_natural_and_physical_sciences) |> mutate(Discipline = "Other Natural and Physical Sciences"),
  as_tibble(future_natural_and_physical_sciences__nfd) |> mutate(Discipline = "Natural and Physical Sciences (n.f.d.)")
)

@@

```{r}
#| label: fig-forecast-total-working-scientists
#| eval: false
#| fig-cap: "Projected total number of working scientists across scientific disciplines from 2022 to 2041. The shaded region represents the 90% prediction interval, the coloured line indicates the mean estimate, and the black line represents historical data."

@@
